Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2024-05-07 manuscript/manuscript.tex
fixed semiparametric

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

@@

\title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
\if0\blind
{
  \author{Mathew Chandy, %\\
%   \href{mailto:mathew.chandy@uconn.edu}
%   {\nolinkurl{mathew.chandy@uconn.edu}}\\
  Elizabeth Schifano\\
  Jun Yan\\
  Xianyang Zhang\\
} \fi

@@

>>>>>>> 8ae0002af5827811aa9091e769fc16303007bc1c

@@

Using R packages \textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2},
we constructed Q-Q plots of the distribution of the p-values to see if they are
uniformly distributed. If the distribution of the p-values is uniform, the
points will be aligned with the diagonal line. This 
indicates that under the null hypothesis, our method will only reject the $H_0$
at the rate of the significance level.
\jy{Describe the table not zoomed-in figure.}
A zoomed in plot for probabilities between 0 and 0.1 is
also provided, as
that is the most common range for significance levels $\alpha$.

@@

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
the extent to which the p-values are uniformly distributed
is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values moreso than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.
\jy{Summarize findings in bullet points before forming text.}

Under $H_0$, the p-values for the non-parametric block bootstrap KS test are
\jy{The flow doesn't read right from the last paragraph}
uniformly distributed as long as the serial dependence is not too high. 
This is an indication that our method 
holds its size for moderate serial dependence levels.
For such cases, we can expect the probability
of a type 1 error to be approximately equivalent to the significance level.

From Tables~\ref{table:rr_norm} and \ref{table:rr_gamma}, we can observe 
that the rejection rate is close to the significance level
as long as 
Kendall's $\tau$ is less than or equal to 0.5 and a sample size greater
than 100 is used.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.9$ to $0.9$. Using a sample size $n \geq 800$ appears to be sufficient
\jy{What are the findings? summarize bullet points before forming texts.}
when $\tau$ is not too high, but for $\tau \geq 0.75$, all sample sizes 
observed appeared to have less than desirable rejection rates. Results
do not appear to be to different when comparing gamma and normal 
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.

@@

The same analyses were repeated on the daily returns of the S\&P 100 index.
Our method demonstrates more instances where it reaches
different conclusions at the 0.05 significance level compared to other methods.
Our method does not reject the hypothesis that the series conforms to a
Student's $t$ distribution with degrees of freedom $v = 5$, yielding a p-value
of 0.0873. In contrast, \citet{babu2004goodness}'s method yields a p-value of 
0.0368, and \citet{zeimbekakis2022misuses}'s method yields a p-value of 0.03.
conclusions regarding the marginal distribution of the population under 
scrutiny.

>>>>

\newcommand{\jy}[1]{\textcolor{blue}{JY: (#1)}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

@@

\title{Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test}
  \author{Mathew Chandy %\\
%   \href{mailto:mathew.chandy@uconn.edu}
%   {\nolinkurl{mathew.chandy@uconn.edu}}\\
%  Elizabeth Schifano\\
%  Jun Yan\\
%  Xianyang Zhang\\
}

@@

@@

Using R packages \textsl{qqplotr} and \textsl{ggplot2} \citep{qqplotr, ggplot2},
we constructed Q-Q plots of the distribution of the p-values to see if they are
uniformly distributed. If the distribution of the p-values is uniform, the
points will be aligned with the diagonal line. This 
indicates that under the null hypothesis, our method will only reject the $H_0$
at the rate of the significance level.
\jy{Describe the table not zoomed-in figure.}\mc{addressed}
A table of the rejection rates for each scheme
also provided/

@@

From Figures~\ref{fig:normal} and \ref{fig:gamma}, we can observe that 
the extent to which the p-values are uniformly distributed
is dependent on the sample size and the level of serial 
dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ is lower than 0.25. For Kendall's $\tau \geq 0.5$, a sample larger than
$n = 200$ seems necessary for the p-values to be normally distributed. For
Kendall's $\tau \geq 0.75$, a sample larger than $n = 800$ appears to be 
necessary, as the p-values are not aligned with the line in any of the Q-Q 
plots. This
is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ corresponds to
a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.
\jy{Summarize findings in bullet points before forming text.}

From Tables~\ref{table:rr_norm} and \ref{table:rr_gamma}, we can observe 
that the agreement between empirical size (rejection rate)
and nominal size (the
significance level) improves as sample size increases, but for $\tau = -0.75$
and $\tau = 0.75$, a sample size larger than 800 seems to be necessary for that 
agreemet to be reached. Using the criteria of approximate agreement between 
empirical size and nominal size, we can say that our approach is working 
for $-0.25 < \tau < 0.25$ for $n > 100$. However a larger sample size seems 
necessary, greater than 400 perhaps, for $\tau$ as strong as $0.5$. In other
words, for weaker dependence, our method works without need for a particular
large sample size, whereas for moderate dependence, a larger sample size may 
be required. Because $\tau$ is typically less than 0.5, it is still safe to
recommend our method with a smaller sample size.

@@

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted -0.75 and 0.75 from this study because we already 
found that our method doesn't work under the null hypothesis for such high
dependence levels. It appears that rejection rate seems to decline as $\tau$ 
increases. Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in 
rejection rates close to 1 for $0.5 < \tau < 0.5$.
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal 
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.

@@

The same analyses were repeated on the daily returns of the S\&P 100 index.
As shown in Table~\ref{table:SP1004}, 
our method demonstrates more instances where it reaches
different conclusions at the 0.05 significance level compared to other methods.
Our method does not reject the hypothesis that the series conforms to a
Student's $t$ distribution with degrees of freedom $v = 5$, yielding a p-value
of 0.0873. In contrast, \citet{babu2004goodness}'s method yields a p-value of 
0.0368, and \citet{zeimbekakis2022misuses}'s method yields a p-value of 0.03.
conclusions regarding the marginal distribution of the population under 
scrutiny.
